%-------------------------
% Resume in Latex
% Author : Omer Ishag
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Omer Ishag}} & Email: \href{mailto:omer.rayah@gmail.com}{omer.rayah@gmail.com}\\
  \href{https://omertv.site/about}{https://omertv.site} & Mobile: +81-80-4866-4321 \\
  \ & 4-4-16, Aobadai, Meguro, Tokyo, Japan \\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
 \resumeSubHeadingListStart
   \item{
     \textbf{Date of Birth}{: June 6, 1988}
     \hfill
     \textbf{Place of Birth}{: Khartoum, Sudan}
     \hfill
     \textbf{Nationality}{: Japanese}
   }
   \item{
    \textbf{Languages}{: Arabic, English, Japanese.}
  }
 \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Typescript/JavaScript, Python. }
   }
 \resumeSubHeadingListEnd
 \resumeSubHeadingListStart
   \item{
     \textbf{Technologies}{: REST, GraphQL, RDBMS, NoSQL databases, Linux, Git, Node.js, NPM, Yarn, React, React Native, SSR, iOS and Android apps deployment. }
   }
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Tokyo}{Tokyo, Japan}
      {Master of Engineering in Systems Innovation}{Oct. 2012 -- Sep. 2014}
    \resumeSubheading
      {Khartoum University}{Khartoum, Sudan}
      {Bachelor of Science and Engineering in Petroleum Engineering}{Sep. 2005 -- Sep. 2010}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Argano}{Shibuya, Tokyo}
      {Software Engineer}{March 2018 - Present}
      \resumeItemListStart
        \resumeItem{Geolocation Service}
          {I was a team member for this mobile application built for iOS and Android. It allows users to browse and post stories. User-generated content includes text, images, and geo-location data. My teammates and I contributed to all parts of the project. Technologies used include REST API, MySQL, Docker, Kubernetes, Elasticsearch, gRPC, Redis, and Firebase (Functions, Firestore).}
        \resumeItem{Social Game}
          {I used the Node.js cluster module to implement a task parallelization feature, which enabled processing players' scores and calculating their ranks quickly.}
          \resumeItem{Ecommerce Application}
          {I contributed to the customer-facing website code, as well as an admin site for managing customers and payments. Among the technologies used are WordPress, Hyperapp, Express.js, Stripe Payments, MySQL, Docker, and AWS.}
        \resumeItem{Hotel Booking Management Application}
          {I contributed to the frontend of the service using React.js and Next.js for SSR.}
          \resumeItem{Browser Automation}
          {I created a React application for this browser automation PoC version.}
        \resumeItem{Browser Extension}
          {I was the manager and the main contributor to this browser extension, which allows users to create customized reports from their analytics data. }
          \resumeItem{Cloud Storage of Personal Data}
          {I was a team member for this paid service, which provides storing information online in a secure way. I contributed to the frontend and backend, using technologies such as GraphQL, Typeorm, MySQL, S3, React, and Next.js. }
        \resumeItem{Tourism Service}
          {I contributed to this e-commerce site built on top of Shopify APIs, with technologies including, GraphQL and React.}
        \resumeItem{PWA}
          {I contributed to this progressive web app (PWA), built  with React and integrated with a serverless-backend architecture using Firebase Functions, Storage and Database, to handle data and light background processing.}
          \resumeItem{GraphQL Codegen Documents}
          {I co-authored this open-source plugin for GraphQL-Codegen. https://github.com/argano/graphql-codegen-documents. }
      \resumeItemListEnd

    \resumeSubheading
      {RCS Corporation}{Chiyoda, Tokyo}
      {Assistant Language Teacher}{May 2015 - March 2018}
      \resumeItemListStart
          {I worked at primary schools in Chiyoda City, and collaborated with Japanese home-room teachers to improve the quality of English language classes.}
      \resumeItemListEnd

      \resumeSubheading
      {Khartoum University}{Khartoum, Sudan}
      {Teaching Assistant}{Sep. 2010 - Sep. 2011}
      \resumeItemListStart
        {I assisted professors with their instructional responsibilities. My tasks included tutoring, preparing tests, and other administrative work.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
